---
title: "Data Science Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# R Programming

## Loop Functions


- lapply: Loop over a **list** and evaluate a function on each element

- sapply: Same as lapply but try simplify the result

- apply: Apply a function over the margins of an array

- tapply(table apply): Apply a function over subsets of a vector

- mapply: Multivariate version of apply

### lapply

lapply **always** return a list, regardless of the class of the input

```{r}
x <- list(a = 1:4, b = rnorm(10), c = rnorm(20, 1), d = rnorm(100, 5))
lapply(x, mean)
```
```{r}
x <- 1:4
lapply(x, runif) # runif:生成给定个数的随机数
```
```{r}
x <- 1:4
lapply(x, runif, min = 0, max = 10) # 设定最小值和最大值
```

lapply and friends make heavy use of *anonymous* functions.

```{r}
x <- list(a = matrix(data = 1:4, nrow = 2, ncol = 2), b = matrix(1:6, 3, 2))
lapply(x, function(elt) elt[,1])
```

### sapply

sapply will to simplify the result of lapply if possible

- If the result is a list where every element is length 1, then a vector is returned.

- If the result is a list where every element is a vecotr of the same length (>1), a matrix is returned.

- If it can't figure things out,a list is returned.


```{r}
x <- list(a = 1:4, b = rnorm(10), c = rnorm(20,1), d = rnorm(100,5))
sapply(x, mean)
```

### apply

apply is userd to a evaluate function (often an anoymous one) over the margins of an array

- It is most often used to apply a function to the rows or columns of a matrix

- It can be used with general arrays, e.g. taking the average of an array of matrices

- It is not really faster than writing a loop, but it works in one line!


```{r}
str(apply)
```

- X is an array

- **MARGIN** is an integer vector indicating which margins should be "retained"

- **FUN** is a function to be applied

- ... is for other auguments to be passed to FUN


```{r}
x <- matrix(rnorm(200), 20, 10)

# 2 means the second dimension
apply(x, 2, mean) # calculate the mean of each columns of the matrix
```

```{r}
apply(x, 1, sum) # the sum of each rows of the matrix
```
#### col/row sums and means

For sums and means of matrix dimensions, we have some shortcuts.

- rowSums = apply(x, 1, sum)

- rowMeans = apply(x, 1, mean)

- colSums = apply(x, 2, sum)

- colMeans = apply(x, 2, mean)

The shortcut function are *much* faster, but you won't notice unless you're using a large matrix.

#### Other ways to Apply

Quantiles of the rows of a matrix

```{r}
x <- matrix(rnorm(200), 20, 10)
apply(x, 1, quantile, probs = c(0.25, 0.75))
```

Average matrix in an array

```{r}
a <- array(rnorm(2 * 2 * 10), c(2, 2, 10))
apply(a, c(1,2), mean)
```


```{r}
rowMeans(a, dim = 2)
```


### mapply

**mapply** is a multivariate apply of sorts which applies a function in parallel over a set of arguments.

```{r}
str(mapply)
```
- **FUN** is a function to apply
- ... contains arguments to apply over
- **MoreArgs** is a list of other arguments to **FUN**
- **SIMPLIFY** indicates wheather the result should be simplified  

The following is tedious to type

```{r}
list(rep(1, 4), rep(2, 3), rep(3, 2), rep(4, 1))
```

Instead we can do

```{r}
mapply(rep, 1:4, 4:1)
```

#### Vectorizing a Function

```{r}
noise <- function(n, mean, sd) {
    rnorm(n, mean, sd)
}
```

```{r}
noise(5, 1, 2)
```

```{r}
noise(1:5, 1:5, 2)
```
显然以上不是我们想要的结果

#### Instant Vectorization

```{r}
mapply(noise, 1:5, 1:5, 2)
```

```{r}
?factor
```


### tapply

**tapply** is used to apply a function over subsets of a vector.  

(Don't know why it's called **tapply*.)

```{r}
str(apply)
```
- **X** is a vector
- **INDEX** is a factor or a list of factors (or else they are coerced to factor)
- **FUN** is a fucntion to be applied
- .. contains other arguments to be passed **FUN**
- **simplify**, should we simplify the result?

Take group means.

```{r}
x <- c(rnorm(10), runif(10), rnorm(10, 1))
f <- gl(3, 10)
f
```
```{r}
tapply(x, f, mean)
```

Take group means without simplification.

```{r}
tapply(x, f, mean, simplify = FALSE)
```

Find group ranges.

```{r}
tapply(x, f, range) # gives the min and the max of the observations within the subsets of the vector x
``` 

### split

split takes a vector or other objects and split it into groups determined by a factor or list of factors.

split is not a loop function but it is a very handy function that can be used in conjuction with functions like lapply.

```{r}
str(split)
```

- **x** is a vector (or list) or data frame
- **f** is a factor (or coerced to one) or a list of factor
- **drop** indicates whether empty factors levels should be dropped

```{r}
x <- c(rnorm(10), runif(10), rnorm(10, 1))
f <- gl(3, 10)
split(x, f)
```

```{r}
lapply(split(x, f), mean)
```


```{r}
tapply(x, f, mean)
```
#### Splitting a Data Frame

```{r}
library(datasets)
head(airquality)
```

```{r}
s <- split(airquality, airquality$Month)
lapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")]))
```

```{r}
sapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")]))
```

```{r}
sapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")], na.rm = TRUE))
```

#### Splitting on More than One Level

```{r}
x <- rnorm(10)
f1 <- gl(2, 5)
f2 <- gl(5, 2)
f1
```
```{r}
f2
```

```{r}
interaction(f1, f2)
```


```{r}
interaction(f1, f2) # 十个factor一一对应左右对应组合起来的结果
```

Interactions can create empty levels.

```{r}
str(split(x, list(f1, f2)))
```

Empty levels can be dropped.

```{r}
str(split(x, list(f1, f2), drop = TRUE))
```
```{r}
list(f1, f2)
```

### Debugging Tools in R

The primary tools for debugging functions in R are

- **traceback**: prints out the function call stack after an error occurs; does nothing if there's no error
- **debug**: flags a function for "debug" mode which allows you to step through execution of a function one line at a time
- **browser**: suspends the execution of a function wherever it is called and puts the function in debug mode
- **trace**: allows you to insert debugging code into a function a specific places
- **recover**: allows you to modify the error behavior so that you can browse the function call stack


#### trackback

当发生错误时，traceback打印出错函数的函数调用栈

```{r}
# mean(z)
```
```{r}
traceback()
```

```{r}
# lm(y - x)
```

```{r}
traceback()
```

#### debug

```{r}
debug(lm)
```

```{r}
# lm(z - y)
```

此时调用lm函数，会先打印出整个函数的代码，然后进入browse模式，可以一行一行的执行代码，定位具体出错的位置。

#### recover

可以通过options()把recover函数设为错误处理器

```{r}
options(error = recover)
```

```{r}
#read.csv("nosuchfile")
```






